Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-21 JASA-template.tex
More edits in intro.

The Bayesian approach in causal effect estimation is a popular
strategy in the field and one of the earlier works on this can be
found in \cite{rubin1978}. Lately, with the rise of high dimensional 
data, Bayesian methodologies have become
more appealing. Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
Bayesian model averaging based method for estimating the causal 
effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
confounding) where they use an informative prior obtained from
the treatment model and apply them on the outcome model for
estimating causal effect. Several other methods were also
proposed to tackle confounders from the point of view of Bayesian
variable selection, see for instance \cite{Zigler2014,Hahn2018} among others.

>>>>

One of the earlier Bayesian approaches to causal inference
can be found in \cite{rubin1978}. More recently,
with the rise of high dimensional data,
Bayesian methodologies have grown in popularity.
Crainiceanu \text{et al.~}\cite{Crainiceanu2008} proposed a bi-level 
Bayesian model averaging based method for estimating the causal 
effect. Wang \text{et al.~}\cite{wang2015} suggested BAC (or, Bayesian adjustment for
confounding), where an informative prior obtained from
the treatment model is applied on the outcome model for
estimating the causal effect. Several other methods were
proposed to tackle confounders from a Bayesian perspective,
see for instance \cite{Zigler2014,Hahn2018} among others.
